\documentclass[overlapped,centered]{res}
\usepackage{xcolor}
\topmargin=-0.5in
\hoffset=1.0in
\setlength{\textheight}{15in}
\definecolor{day9yellow}{HTML}{FFA71A}
\begin{document}
\name{\textcolor{day9yellow}{Tom} Pedraza\\[10pt]}
\address{{\bf Contact Info} \\ LunarSC95@gmail.com\\(336) 207-5532\\tompedraza.com\\github.com/LunarSC }
\address{{}}

\begin{resume}

\section{EDUCATION}
\vphantom0
\begin{tabular}{p{3in} r}
                  University of North Carolina Greensboro
                  \end{tabular}
                   \begin{itemize}
                    \item[] Bachelor of Science in Computer Science, July 2018
		\item[] National Computer Science ETS exam score of the 80th percentile
		   \end{itemize}

\noindent\rule{12cm}{0.4pt}

                \begin{ncolumn}{3}
                {\bf Proficient Languages}   &  {\bf Comfortable Languages} & {\bf Other}\\
                Java             &  SQL             & REST\\
                C\# 	     &  Python              & SOAP\\
                HTML            &  PHP              & Full Stack\\
                CSS              &  C 		& ReactJS\\
                XML	    & Javascript \\
		\end{ncolumn}

\noindent\rule{12cm}{0.4pt}

\section{EXPERIENCE}
\vphantom0
		\begin{tabular}{p{3in}r}
		Qualitest & June 2018 -- May 2019
		\end{tabular}
		\begin{itemize}
		\item[] -- Automation Quality Assurance Tester
		\item[] Demonstrated object oriented programming skills in an enterprise \\ environment.
		\item[] Developed automated scripts using VBScript, Java, and Selenium \\ for software regression testing.
		\item[] Tested websites and web services produced by Commerce Bank's developers \\ to ensure high software standards, security, and usability.
		\item[] Worked as a team with others performing testing sprints; High \\ intensity, focused, and specific goals.
		\item[] Communicated with upper management and with team developers \\ in a professional manner to receive instructions and provide reports.
		\end{itemize}

		 \begin{tabular}{p{3in} r}
                  UNCG Computer Science Department &  January 2018 -- May 2018
                 \end{tabular}
		 \begin{itemize}
		\item[] -- Student Lab Assistant
                \item[] Assisted dozens of students with learning and \\ applying Java related programming skills.
		\item[] Abstracted core computer science concepts to \\ provide students with  valuable and relevant information.
                \end{itemize}

                \begin{tabular}{p{3in} r}
                UNCG 6-TECH Information Technology Support & June 2016 -- November 2017
                \end{tabular}
                \begin{itemize}
		\item[] -- IT Help Desk -- Student Analyst
                \item[] Provided email support, account recovery, and other UNCG technical services.
		\item[] Communicated effectively with a diverse group of students.
		 \end{itemize}




\noindent\rule{12cm}{0.4pt}

\section{HOBBIES\\}\vphantom0  Programming, physical fitness, and competitive gaming

\end{resume}
\end{document}
